### 2019-11-22 3_implementation.tex
Edits to the implementation section.

Charm++~\cite{Charmpp93} is an explicitly parallel actor-based programming system. Actors(
\emph{chares}) are objects in their own address space.
Chares communicate data and synchronize via messages and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column. Messages implement dependencies; a task executes as soon as its
dependencies are all available.

@@

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of point-to-point communication with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI. We also provide a bulk synchronous
implementation which enforces the boundary between communication and
computation with \lstinline[language=C++]{MPI_Barrier}.

@@

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hierarchical programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks,
interleaved with MPI point-to-point communication as above. Our
MPI+CUDA implementation follows an offload model where data is copied
to and from the GPU on every timestep.

\subsection{OmpSs and OpenMP}

OmpSs~\cite{OmpSs11} and OpenMP~\cite{OpenMPSpec40} are programming
models for loop- and task-based parallelism. (OpenMP is
source-compatible with OmpSs.) The implementations use OpenMP 4.0
tasking.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. For OpenMP, we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. To
improve scalability, the program is executed in
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of HPC workflows. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}. 
Our Task Bench in Swift/T uses it's dataflow
semantics to capture dependencies on other tasks.

>>>>

Charm++~\cite{Charmpp93} is an explicitly parallel actor-based programming system. Actors
(\emph{chares}) do not share memory and communicate via messages. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column, and uses messages to implement dependencies.

@@

We provide two MPI~\cite{MPI} implementations, written in the style of
communicating sequential processes (CSP) and bulk synchronous
programming (BSP), respectively. An excerpt from the CSP
implementation is shown in Listing~\ref{lst:code-sample}. The BSP
implementation uses \lstinline[language=C++]{MPI_Barrier} to enforce
boundaries between phases.

@@

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hierarchical programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks, but
otherwise follows the CSP implementation above. The code uses shared
memory for data movement within a rank. Our MPI+CUDA implementation
follows an offload model where data is copied to and from the GPU on
every timestep.

\subsection{OpenMP and OmpSs}

OpenMP~\cite{OpenMPSpec40} and OmpSs~\cite{OmpSs11} are programming
models for loop- and task-based parallelism. (OmpSs is
source-compatible with OpenMP.) The implementations use OpenMP 4.0
tasking.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. For OpenMP, we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

In the DTD model, tasks are enumerated in program order (by executing
the program), and dependencies are identified automatically based on
the arguments to tasks. To improve scalability, the program is
executed in SPMD fashion on all nodes, and the user is responsible for
eliding tasks that are not direct predecessors or successors to those
executed on the current node.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of HPC workflows. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}. 
Our Task Bench in Swift/T uses its dataflow
semantics to capture dependencies on other tasks.
